Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
Some corrections in future work sections

The largest limitation to our current work is the the QRR.  In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.  However, a significant amount user interaction is required to understand the answer retrieval process.  By continuing to studying the methods of user data collection we plan to develop a model to support a unsupervised question resolution process.  This will increase the scalability and efficiency of the system.

@@

Currently, the category hierarchy that is generated from the DBpedia categories and our SSQ ontologies are stored in separate XML files. We are in the process of storing these ontologies into an efficient ontology database. Similarly, employing user input brings about the likelihood that redundant SSQ ontological elements will be inserted into our ontology store. We are working on merging the similar SSQs [\label{sec:ssq}] based on the SSQ realms and other ontological structural information so that we can remove the redundancy in the database.

@@

Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.  We believe that an even higher number of those are parametrizable, meaning, a set of queries are all related and may be answered using a single QRM.  It is difficult to discover this property.  Previous work suggest techniques to find related queries but it will take a new method to discover parametrizable queries.

@@

In this paper we provide a discussion on a new type of question answering system that uses previously answered questions user.  We described our method of modelling a users question answering process and how we are able to discover semantically similar queries.

>>>>

The largest limitation to our current work is the QRR.  In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.  However, a significant amount user interaction is required to understand the answer retrieval process.  By continuing to studying the methods of user data collection we plan to develop a model to support a unsupervised question resolution process.  This will increase the scalability and efficiency of the system.

@@

Currently, the category hierarchy that is generated from the DBpedia categories and our SSQ ontologies are stored in separate XML files. We are in the process of storing these ontologies into an efficient ontology database. Similarly, employing user input brings about the likelihood that redundant SSQ ontological elements will be inserted into our ontology store. We are working on merging the similar SSQs [\ref{sec:ssq}] based on the SSQ realms and other ontological structural information so that we can remove the redundancy in the database.

@@

Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.  We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.  It is difficult to discover this property.  Previous work suggest techniques to find related queries but it will take a new method to discover parameterizable queries.

@@

In this paper we provide a discussion on a new type of question answering system that uses previously answered questions user.  We described our method of modeling a users question answering process and how we are able to discover semantically similar queries.
